---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```
# snapapps

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/snapapps.svg?branch=master)](https://travis-ci.org/leonawicz/snapapps)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/snapapps?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/snapapps)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/snapapps/master.svg)](https://codecov.io/github/leonawicz/snapapps?branch=master)

The `snapapps` package contains a collection of open source Shiny apps by Matthew Leonawicz at the Scenarios Network for Alaska and Arctic Planning, University of Alaska Fairbanks. It is a member package in the apps and docs sector of the SNAPverse collection of R packages. Many of the apps in this package originate from the SNAP open source Shiny apps [GitHub repository](https://github.com/ua-snap/shiny-apps). Additional apps can be found in other SNAPverse apps and docs sector packages. Related sector packages include `snapdash`, `snapflex` and `snapdocs`.

## Installation

You can install snapapps from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snapapps")
```
